Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2024-08-08 paper/main.tex
Updates

\todo[inline]{Add an example here showing these problems}

@@

A common method for specification search is using \emph{modification indices},
which identify potential changes to the model structure that improve the model
fit. These potential changes are then ranked by the ones that improve the fit
the most. This ranking allows the researchers to focus first on the suggestions
that can improve the model the most and while integrating their expertise to
choose the most optimal modifications. Inspired by this ranking approach in
modification indices, in this paper we develop a method to rank the CI tests
using a conditional measure of association. Our proposed approach uses the
measure of association to find correlated variables in the data that are not
explained by the current model. Using the measure, we can then rank the pair of
variables between which adding an edge would improve the explanation the most.
Based on this information, the user can select a potential pair of variables
and based on their expert knowledge decide the direction of the edge. 
\todo[inline]{Add about the score based methods somewhere here}

Our main contributions in this paper are as follows:
\begin{enumerate}
	\item We present a measure of (conditional) association for mixed data
		based on canonical correlations. This measure of association
		generalizes the widely used partial correlation to mixed data
		setting.
	\item Using this partial association measure, we present a procedure to
		rank CI tests. This ranking can be used to prioritize addition
		or deletion of edges from the model.
	\item Lastly, we present a web-browser based tool to allow researchers
		to apply this method to their own datasets.
\end{enumerate}

>>>>

@@

A common method for specification search is using \emph{modification indices},
which identify potential changes to the model structure that improve the model
fit. These potential changes are then ranked by the ones that improve the fit
the most. This ranking allows the researchers to focus first on the suggestions
that can improve the model the most and while integrating their expertise to
choose the most optimal modifications. Inspired by this ranking approach in
modification indices, in this paper we develop a method to rank the CI tests
using a conditional measure of association. Our proposed approach uses the
measure of association to find correlated variables in the data that are not
explained by the current model. Using the measure, we can then rank the pair of
variables between which adding an edge would improve the explanation the most.
Based on this information, the user can select a potential pair of variables
and based on their expert knowledge decide the direction of the edge.

Our main contributions in this paper are as follows:
\begin{enumerate}
	\item We present a measure of (conditional) association for mixed data
		based on canonical correlations. This measure of association
		generalizes the widely used partial correlation to mixed data
		setting.
	\item Using this partial association measure, we present a procedure to
		rank CI tests. This ranking can be used to prioritize addition
		or deletion of edges from the model.
	\item Lastly, we present a both a web-browser based tool and an
		implementation in the Python package to allow researchers to
		apply this method to their own datasets.
\end{enumerate}
